---
format:
  dashboard:
    orientation: columns
    scrolling: true
---

```{r}
#| message: FALSE
library(flowCore)
library(dplyr)
library(purrr)
library(stringr)
library(plotly)
library(Luciernaga)

Computer <- getwd()
MainFolder <- file.path(Computer, "data")
TheList <- c("Attune1")

# RMI - It should be possible to copy the required QC files to the J: or Z: drive we could then use this as the MainFolder
# MainFolder <- "/home/david/Documents/InstrumentQC/data"

CSTGates <- file.path(Computer, "Gates.csv")

# Updating Data (Work through later)
walk(.x=TheList, .f=Luciernaga:::HolisticQCParse, MainFolder=MainFolder, Template=CSTGates, subsets="Staining")
```

```{r}
#MainFolder <- "/home/david/Documents/InstrumentQC/data"
Attune1Data <- Luciernaga:::CurrentData(x=TheList, MainFolder=MainFolder, type = "Both")
TheDate <- Attune1Data %>% slice(1) %>% pull(DATE)
```

```{r}
WindowOfInterest <- Sys.time() - months(24)

Both_Attune1 <- Attune1Data %>% filter(DateTime >= WindowOfInterest)
```

```{r}
# RMI this routine is loading in a maintenance log and potentially adding to it Comment out for now 04262026

# Data <- read.csv("AuroraMaintenance.csv", check.names=FALSE)
# 
# #Data <- read.csv("/home/david/Documents/InstrumentQC/AuroraMaintenance.csv", check.names=FALSE)
# 
# Data <- Data %>% filter(!str_detect(reason, "lean"))
# 
# RepairAttune1 <- Data %>% filter(instrument %in% "Attune1")
# Maintenance <- RepairAttune1
```

```{r}
x <- Both_Attune1
TheColumns <- x %>% select(where(~is.numeric(.)||is.integer(.))) %>% colnames()
TheColumns <- setdiff(TheColumns, "TIME")

# MFIs
TheIntermediate <- TheColumns[!str_detect(TheColumns, "Gain")]
TheIntermediate <- TheIntermediate[!str_detect(TheIntermediate, "rCV")]
TheColumnNames <- TheIntermediate[str_detect(TheIntermediate, "-A")]
  
VioletGains <- TheColumnNames[str_detect(TheColumnNames, "^V")]
BlueGains <- TheColumnNames[str_detect(TheColumnNames, "^B")]
YellowGreenGains <- TheColumnNames[str_detect(TheColumnNames, "^Y")]
RedGains <- TheColumnNames[str_detect(TheColumnNames, "^R")]

ScatterGains <- TheIntermediate[str_detect(TheIntermediate, "SC-")]
ScatterGains <- Luciernaga:::ScalePriority(ScatterGains)
LaserGains <- TheIntermediate[str_detect(TheIntermediate, "Laser")]
LaserGains <- Luciernaga:::ColorPriority(LaserGains)
ScalingGains <- TheIntermediate[str_detect(TheIntermediate, "Scaling")]
ScalingGains <- Luciernaga:::ColorPriority(ScalingGains)
OtherGains <- c(ScatterGains, LaserGains, ScalingGains)

VioletPlotsMFI <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=VioletGains,
                      plotType = "individual", returntype = "plots",
                      Metadata="NULL", strict = TRUE, YAxisLabel = "MFI",
                      RepairVisits=RepairAttune1)

BluePlotsMFI <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=BlueGains,
                      plotType = "individual", returntype = "plots",
                      Metadata=NULL, strict = TRUE, YAxisLabel = "MFI",
                      RepairVisits=RepairAttune1)

YellowGreenPlotsMFI <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=YellowGreenGains,
                     plotType = "individual", returntype = "plots",
                     Metadata=NULL, strict = TRUE, YAxisLabel = "MFI",
                     RepairVisits=RepairAttune1)                      

RedPlotsMFI <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=RedGains,
                     plotType = "individual", returntype = "plots",
                     Metadata=NULL, strict = TRUE, YAxisLabel = "MFI",
                     RepairVisits=RepairAttune1)

ScatterPlotsMFI <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=ScatterGains,
                     plotType = "individual", returntype = "plots",
                     Metadata=NULL, strict = TRUE, YAxisLabel = " ",
                     RepairVisits=RepairAttune1)

LaserPlotsMFI <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=LaserGains,
                     plotType = "individual", returntype = "plots",
                     Metadata=NULL, strict = TRUE, YAxisLabel = " ",
                     RepairVisits=RepairAttune1)
```


```{r}
TheColumns <- x %>% select(where(~is.numeric(.)||is.integer(.))) %>% colnames()
TheColumns <- setdiff(TheColumns, "TIME")

# RCVs
TheIntermediate <- TheColumns[!str_detect(TheColumns, "Gain")]
TheIntermediate <- TheIntermediate[str_detect(TheIntermediate, "rCV")]
TheColumnNames <- TheIntermediate[str_detect(TheIntermediate, "-A")]
  
VioletGains <- TheColumnNames[str_detect(TheColumnNames, "^V")]
BlueGains <- TheColumnNames[str_detect(TheColumnNames, "^B")]
YellowGreenGains <- TheColumnNames[str_detect(TheColumnNames, "^Y")]
RedGains <- TheColumnNames[str_detect(TheColumnNames, "^R")]

ScatterGains <- TheIntermediate[str_detect(TheIntermediate, "SC-")]
ScatterGains <- Luciernaga:::ScalePriority(ScatterGains)
LaserGains <- TheIntermediate[str_detect(TheIntermediate, "Laser")]
LaserGains <- Luciernaga:::ColorPriority(LaserGains)
ScalingGains <- TheIntermediate[str_detect(TheIntermediate, "Scaling")]
ScalingGains <- Luciernaga:::ColorPriority(ScalingGains)
OtherGains <- c(ScatterGains, LaserGains, ScalingGains)

VioletPlotsRCV <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=VioletGains,
                      plotType = "individual", returntype = "plots", YAxisLabel = "%rCV",
                      RepairVisits=Maintenance)

BluePlotsRCV <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=BlueGains,
                      plotType = "individual", returntype = "plots", YAxisLabel = "%rCV",
                      RepairVisits=Maintenance)

YellowGreenPlotsRCV <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=YellowGreenGains,
                      plotType = "individual", returntype = "plots", YAxisLabel = "%rCV",
                      RepairVisits=Maintenance)

RedPlotsRCV <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=RedGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = "%rCV",
                     RepairVisits=Maintenance)

ScatterPlotsRCV <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=ScatterGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = " ",
                     RepairVisits=Maintenance)
```

```{r}
x <- Both_Attune1
TheColumns <- x %>% select(where(~is.numeric(.)||is.integer(.))) %>% colnames()
TheColumns <- setdiff(TheColumns, "TIME")

# Gains
TheColumnNames <- TheColumns[str_detect(TheColumns, "Gain")]
TheColumnNames <- TheColumnNames[str_detect(TheColumnNames, "-A")]

VioletGains <- TheColumnNames[str_detect(TheColumnNames, "^V")]
BlueGains <- TheColumnNames[str_detect(TheColumnNames, "^B")]
YellowGreenGains <- TheColumnNames[str_detect(TheColumnNames, "^Y")]
RedGains <- TheColumnNames[str_detect(TheColumnNames, "^R")]

ScatterGains <- TheColumnNames[str_detect(TheColumnNames, "SC-")]
ScatterGains <- Luciernaga:::ScalePriority(ScatterGains)
LaserGains <- TheColumns[str_detect(TheColumns, "Laser")]
LaserGains <- Luciernaga:::ColorPriority(LaserGains)
ScalingGains <- TheColumns[str_detect(TheColumns, "Scaling")]
ScalingGains <- Luciernaga:::ColorPriority(ScalingGains)
OtherGains <- c(ScatterGains, LaserGains, ScalingGains)

VioletPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=VioletGains,
                      plotType = "individual", returntype = "plots", YAxisLabel = "Gain",
                      RepairVisits=RepairAttune1)

BluePlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=BlueGains,
                      plotType = "individual", returntype = "plots", YAxisLabel = "Gain",
                      RepairVisits=RepairAttune1)

YellowGreenPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=YellowGreenGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = "Gain",
                     RepairVisits=RepairAttune1)


RedPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=RedGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = "Gain",
                     RepairVisits=RepairAttune1)

ScatterPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=ScatterGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = " ",
                     RepairVisits=RepairAttune1)

LaserPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=LaserGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = " ",
                     RepairVisits=RepairAttune1)

ScalingPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=ScalingGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = " ",
                     RepairVisits=RepairAttune1)
```

```{r}
#| include: false
#| echo: false
PDFPlots <- c(VioletPlotsMFI, BluePlotsMFI, YellowGreenPlotsMFI, RedPlotsMFI, ScatterPlotsMFI, VioletPlotsGain, BluePlotsGain, YellowGreenPlotsGain, RedPlotsGain, ScatterPlotsGain, LaserPlotsGain, ScalingPlotsGain, VioletPlotsRCV, BluePlotsRCV, YellowGreenPlotsRCV, RedPlotsRCV, ScatterPlotsRCV)

Filename <- paste0("QCPlots_Attune1")

PDF <- Utility_Patchwork(x=PDFPlots, filename=Filename, returntype="pdf", outfolder=MainFolder, thecolumns=1)
```

## {.sidebar}
Dashboard data for the **Attune1 II** last updated on **`r TheDate`**

**First Column: MFI** Median Fluorescent Intensity (MFI) values for the QC beads. Measures stability over time. 


**Second Column: Gain** Gain (Voltage) values set for instrument after QC. Changes over time reflective of laser health. 

**Third Colum: RCV** Percentage change of Robust Coefficient VAttune1tion (RCV) after QC. Higher values reflect decreased resolution between positive and negative for that detector.

For additional information concerning individual parameter tabs, navigate to the [Help](https://umgccfcss.github.io/InstrumentQC/help) page.

**About**

This dashboard contains the visualized QC data for the Cytek and BD cytometers at the [UMGCC FCSS](https://www.medschool.umaryland.edu/cibr/core/umgccc_flow/)

For additional flow cytometry resources, visit our [website](https://sites.google.com/view/umgcccflow/home)

This dashboard was created with [Quarto](https://quarto.org/) and is maintained by [David Rach](https://github.com/DavidRach)

## MFI {.tabset}

```{r}
#| title: Violet
ggplotly(VioletPlotsMFI[[1]])
ggplotly(VioletPlotsMFI[[2]])
ggplotly(VioletPlotsMFI[[3]])
```

```{r}
#| title: Blue
ggplotly(BluePlotsMFI[[1]])
ggplotly(BluePlotsMFI[[2]])
```

```{r}
#| title: YellowGreen
ggplotly(YellowGreenPlotsMFI[[1]])
ggplotly(YellowGreenPlotsMFI[[2]])
ggplotly(YellowGreenPlotsMFI[[3]])
ggplotly(YellowGreenPlotsMFI[[4]])
```

```{r}
#| title: Red
ggplotly(RedPlotsMFI[[1]])
ggplotly(RedPlotsMFI[[2]])
```

```{r}
#| title: Scatter
ggplotly(ScatterPlotsMFI[[1]])
ggplotly(ScatterPlotsMFI[[2]])
ggplotly(ScatterPlotsMFI[[3]])
ggplotly(ScatterPlotsMFI[[4]])
ggplotly(ScatterPlotsMFI[[5]])
ggplotly(ScatterPlotsMFI[[6]])
```

```{r}
#| title: LaserDelay
ggplotly(LaserPlotsGain[[1]])
ggplotly(LaserPlotsGain[[2]])
ggplotly(LaserPlotsGain[[3]])
ggplotly(LaserPlotsGain[[4]])
```

```{r}
#| title: LaserScaling
ggplotly(ScalingPlotsGain[[1]])
ggplotly(ScalingPlotsGain[[2]])
ggplotly(ScalingPlotsGain[[3]])
ggplotly(ScalingPlotsGain[[4]])
```

## Gain {.tabset}

```{r}
#| title: Violet
ggplotly(VioletPlotsGain[[1]])
ggplotly(VioletPlotsGain[[2]])
ggplotly(VioletPlotsGain[[3]])
```

```{r}
#| title: Blue
ggplotly(BluePlotsGain[[1]])
ggplotly(BluePlotsGain[[2]])
```

```{r}
#| title: YellowGreen
ggplotly(YellowGreenPlotsGain[[1]])
ggplotly(YellowGreenPlotsGain[[2]])
ggplotly(YellowGreenPlotsGain[[3]])
ggplotly(YellowGreenPlotsGain[[4]])
```

```{r}
#| title: Red
ggplotly(RedPlotsGain[[1]])
ggplotly(RedPlotsGain[[2]])
```

```{r}
#| title: Scatter
ggplotly(ScatterPlotsGain[[1]])
ggplotly(LaserPlotsGain[[2]])
ggplotly(LaserPlotsGain[[2]])
ggplotly(ScatterPlotsGain[[2]])
ggplotly(LaserPlotsGain[[2]])
ggplotly(LaserPlotsGain[[2]])
```

```{r}
#| title: LaserDelay
ggplotly(LaserPlotsGain[[1]])
ggplotly(LaserPlotsGain[[2]])
ggplotly(LaserPlotsGain[[3]])
ggplotly(LaserPlotsGain[[4]])
```

```{r}
#| title: LaserScaling
ggplotly(ScalingPlotsGain[[1]])
ggplotly(ScalingPlotsGain[[2]])
ggplotly(ScalingPlotsGain[[3]])
ggplotly(ScalingPlotsGain[[4]])
```

## rCV {.tabset}

```{r}
#| title: Violet
ggplotly(VioletPlotsRCV[[1]])
ggplotly(VioletPlotsRCV[[2]])
ggplotly(VioletPlotsRCV[[3]])
```

```{r}
#| title: Blue
ggplotly(BluePlotsRCV[[1]])
ggplotly(BluePlotsRCV[[2]])
```

```{r}
#| title: YellowGreen
ggplotly(YellowGreenPlotsRCV[[1]])
ggplotly(YellowGreenPlotsRCV[[2]])
ggplotly(YellowGreenPlotsRCV[[3]])
ggplotly(YellowGreenPlotsRCV[[4]])
```

```{r}
#| title: Red
ggplotly(RedPlotsRCV[[1]])
ggplotly(RedPlotsRCV[[2]])
```

```{r}
#| title: Scatter
ggplotly(ScatterPlotsRCV[[1]])
ggplotly(ScatterPlotsRCV[[2]])
ggplotly(ScatterPlotsRCV[[3]])
ggplotly(ScatterPlotsRCV[[4]])
ggplotly(ScatterPlotsRCV[[5]])
ggplotly(ScatterPlotsRCV[[6]])
```

```{r}
#| eval: TRUE
#| title: LaserPower
ggplotly(LaserPlotsGain[[1]])
ggplotly(LaserPlotsGain[[2]])
ggplotly(LaserPlotsGain[[3]])
ggplotly(LaserPlotsGain[[4]])
```

```{r}
#| title: LaserScaling
ggplotly(ScalingPlotsGain[[1]])
ggplotly(ScalingPlotsGain[[2]])
ggplotly(ScalingPlotsGain[[3]])
ggplotly(ScalingPlotsGain[[4]])
```

